# Properties of spatial objects


The following code makes use of two packages:
- the *sf* package, which is available from https://cran.r-project.org/package=sf
- the *units* package, which is available from https://cran.r-project.org/package=units
To run the code of this notebook you can install the packages by `install.packages(c("sf","units"))`. However, they are already installed in the container on which this example is run.


```{r}
library(sf)
```

The files "south-america-1990.RData" and "three-countries.RData" were created in a previous example.

```{r}
load("south-america-1990.RData")
load("three-countries.RData")
```

```{r}
st_area(Brazil)
```

```{r}
in_km2 <- function(x) units::set_units(x,"km^2")
in_km2(st_area(Brazil))
```

```{r}
in_km2(st_area(SthAmCountries))
```

```{r}
structure(in_km2(st_area(SthAmCountries)),
          names=as.character(SthAmCountries$CNTRY_NAME))
```

```{r}
st_distance(Brasilia,Bogota)
```

```{r}
st_distance(Chile,Bogota)
```

```{r}
# This takes a while, because R needs to figure out which points of the borders are the closest to one another
st_distance(Chile,Colombia)
```

```{r}
in_km <- function(x) units::set_units(x,"km")
in_km(st_distance(Brasilia,Bogota))
```

```{r}
in_km(st_distance(ThreeCapitals))
```
