# Creating a "zoo" object from OECD unemployment data


The data file ["unemployment.csv"](https://github.com/melff/dataman-r/raw/main//dates-times-timeseries/OECD-unemployment.R) used below consists of data originally downloaded from the [OECD Database website](https://data.oecd.org).

```{r}
unemployment <- read.csv("unemployment.csv")
```

The following makes use of the *zoo* package. You may need to install it from
[CRAN](https://cran.r-project.org/package=zoo) using the code
`install.packages("zoo")` if you want to run this on your computer. (The
package is already installed on the notebook container, however.)

```{r}
library(zoo)
```

```{r}
unemployment.z <- zoo(unemployment[,2:7],
                      order.by=as.Date(
                          ISOdate(year=unemployment[,1],
                                  month=12,
                                  day=31)))
```

```{r}
dim(unemployment.z)
```

```{r}
class(unemployment.z)
```

```{r}
head(unemployment.z)
```

```{r}
start(unemployment.z)
```

```{r}
end(unemployment.z)
```

```{r}
end(unemployment.z) - start(unemployment.z)
```

```{r}
# Saved for later use:
save(unemployment.z,file="unemployment-z.RData")
```
