# Subsetting data with *dplyr*


The following makes use of the *dplyr* package. You may need to install it
from [CRAN](https://cran.r-project.org/package=data.table) using the code
`install.packages("dplyr")` if you want to run this on your computer. (The package is already installed on
the notebook container, however.)

```{r}
options(jupyter.rich_display=FALSE) # Create output as usual in R
```

Here we use data from the British Election Study 2010. The data set [bes2010feelings.RData](https://github.com/melff/dataman-r/raw/main/data-frames/bes2010feelings.RData) is prepared from the original available at https://www.britishelectionstudy.com/data-object/2010-bes-cross-section/ by removing identifying information and scrambling the data.

```{r}
load("bes2010feelings.RData")
```

```{r}
library(dplyr)
```

```{r}
bes2010feelings.sub <- bes2010feelings %>%
                            filter(region == "Scotland") %>%
                            select(wave,
                                   flng.brown,
                                   flng.cameron,
                                   flng.clegg,
                                   flng.salmond)
```

```{r}
head(bes2010feelings.sub)
```

```{r}

```
