# Filling and completing with *tidyr*

The following makes use of the packages *tidyr* and *readr*. You may need to install them from [CRAN](https://cran.r-project.org) using the code `install.packages(c("tidyr","readr"))` if you want to run this on your computer. 
(The packages are already installed
on the notebook container, however.)

```{r}
options(jupyter.rich_display=FALSE) # Create output as usual in R
```

Filling missing values with `fill()`

```{r}
library(tidyr)
library(readr)
```

```{r}
messy_data_str <- "
country,  year,var1, var2
Rodinia,  1297,  67, -3.0
,         1298,  69, -2.9
,         1299,  70, -2.8
Pannotia, 1296,  73, -4.1
,         1297,  74, -3.9
,         1298,  75, -3.9
Pangaea,  1296,  54, -1.2
,         1297,  53, -1.1
,         1298,  52, -1.0
,         1299,  51, -0.9
"
```

```{r}
messy_data_str %>% read_csv() -> messy_data
messy_data
```

```{r}
messy_data %>% fill(country) -> filled_data
filled_data
```

Completing data by missing values with `complete()`

```{r}
filled_data %>% complete(crossing(country,year))
```

```{r}

```
