# Summarizing data with *dplyr*

```{r}
options(jupyter.rich_display=FALSE) # Create output as usual in R
```

The following makes use of the *dplyr* package. You may need to install it
from [CRAN](https://cran.r-project.org/package=data.table) using the code
`install.packages("dplyr")` if you want to run this on your computer. (The package is already installed on
the notebook container, however.)

```{r}
library(dplyr)
```

Here we use data from the British Election Study 2010. The data set
[bes2010feelings.RData](https://github.com/melff/dataman-r/raw/main/data-frames/bes2010feelings.RData)
is prepared from the original available at
https://www.britishelectionstudy.com/data-object/2010-bes-cross-section/ by
removing identifying information and scrambling the data.

```{r}
load("bes2010feelings.RData")
```

```{r}
# A convenience function
Mean <- function(x,...) mean(x,na.rm=TRUE,...) 
```

```{r}
bes2010feelings %>% group_by(wave,region) %>%
                    summarize(Brown=Mean(flng.brown),
                              Cameron=Mean(flng.cameron),
                              Clegg=Mean(flng.clegg),
                              N=n())
```

```{r}

```
