# Appending data frames


First we load some example data from the British Election Study 2010. The data set [bes2010feelings-for-append.RData](https://github.com/melff/dataman-r/raw/main/data-frames/bes2010feelings-for-append.RData) is prepared from the original available at https://www.britishelectionstudy.com/data-object/2010-bes-cross-section/ by removing identifying information and scrambling the data.

```{r}
load("bes2010feelings-for-append.RData")
```

We now have two BES data frames, one from the pre-election wave and another
from the post-election wave. They contain the same variables, but in a different
order:

```{r}
str(bes2010flngs_pre)
```

```{r}
str(bes2010flngs_post)
```

If the variables in the two data frames differ trying to use `rbind()` to append
the data frames fails.

```{r}
bes2010flngs_prepost <- rbind(bes2010flngs_pre[-1],
                              bes2010flngs_post[-1])
```

If the variables in the two data frame are the same but differ in their order,
`rbind()` succeeds and the variables are sorted all into the same order before the
data frames are combined into a single one:

```{r}
bes2010flngs_prepost <- rbind(bes2010flngs_pre,
                              bes2010flngs_post)
```

We compare the tail-ends of the data resulting data frame
`bes2010flngs_prepost` and the data frame given as second argument to
`rbind`. The tail-ends are identical except for the order of the
variables.

```{r}
options(width=200)
tail(bes2010flngs_prepost)
```

```{r}
tail(bes2010flngs_post)
```
