# Merging data frames: An example with data from the British Election Study

```{r}
options(jupyter.rich_display=FALSE) # Create output as usual in R
```

Here we merge data from the British Election Study. Here we use data from the British Election Study 2010. The data set [bes2010feelings-prepost-for-merge.RData](https://github.com/melff/dataman-r/raw/main/data-frames/bes2010feelings-prepost-for-merge.RData) is prepared from the original available at https://www.britishelectionstudy.com/data-object/2010-bes-cross-section/ by removing identifying information and scrambling the data.

```{r}
load("bes2010feelings-prepost-for-merge.RData")
```

A peek into a data frame about respondents' feelings about
parties:

```{r}
head(bes2010flngs_parties_pre)
```

And anotehr peek into a data frame about respondents' feelings about
party leaders:

```{r}
head(bes2010flngs_leaders_pre)
```

The variable that identifies individual respondents in both
data frames is 'id', so we use this variable to match the
rows in both data frames:

```{r}
bes2010flngs_pre_merged <- merge(
    bes2010flngs_parties_pre,
    bes2010flngs_leaders_pre,
    by="id"
)
```

`merge()` also allows for identifier variables that may have
different names in the two data frame. In such cases
one can use the named arguments `by.x=` and `by.y=`:

```{r}
bes2010flngs_pre_merged <- merge(
    bes2010flngs_parties_pre,
    bes2010flngs_leaders_pre,
    by.x="id",
    by.y="id"
)
```

It is not absolutely necessary to provide a `by=` argument, if
the merged data frames share a variable (with the same name in both)
that idenfies cases or observations. Therefore, we can call `merge()` here without any `by=`, `by.x=`, or `by.y=` arguments:

```{r}
bes2010flngs_pre_merged <- merge(
    bes2010flngs_parties_pre,
    bes2010flngs_leaders_pre
)
head(bes2010flngs_pre_merged)
```

The data frame `constwin` contains data about relectoral districts, that is
which party won the respective district seat in 2005 and 2010. The
variable that identifies the electoral district is both in the individual-level
data frame and the district-level data frame is named `refno`, so we use this
as a matching variable.

```{r}
bes2010pre_merged <- merge(
    bes2010flngs_pre_merged,
    constwin,
    by = "refno" # Not necessary in the present case, because
)                # it is the same in both data frames.
```

As can be glimpsed from the output of `str`, the result of `merge` is
sorted by the matching variable, i.e. "refno"

```{r}
head(bes2010pre_merged)
```

```{r}

```
