# Poststratification of 2016 American National Election Study data


The following data file was created in an earlier script / notebook.

```{r}
load("anes-2016-prevote.RData")
```

There must not be any missing values in the stratifying variables.

```{r}
anes_2016_vprevote <- subset(anes_2016_prevote,
                                    vote16 != "Inap" &
                                    recall12 != "Inap"
                                    )
```

In order to make poststratification possible, we need to make sure that the
levels of the stratification variables match the population
information. Therefore we relabel the variables "recall12" and "vote16".


The following makes use of the *memisc* package. You may need to install it from
[CRAN](https://cran.r-project.org/package=memisc) using the code
`install.packages("memisc")` if you want to run this on your computer. (The
package is already installed on the notebook container, however.)

```{r}
library(memisc)
```

```{r}
anes_2016_vprevote <- within(anes_2016_vprevote,{
    recall12 <- recall12[,drop=TRUE]
    vote16 <- vote16[,drop=TRUE]
    recall12 <- relabel(recall12,"Did not vote"="No vote")
    vote16 <- relabel(vote16,
                      "Will not vote/Not registered"="No vote")
})
save(anes_2016_vprevote,file="anes-2016-vprevote.RData")
```

Finally, we set up a survey design object. The following makes use of the *survey* package. You may need to install it from [CRAN](https://cran.r-project.org/package=survey) using the code
`install.packages("survey")` if you want to run this on your computer. (The
package is already installed on the notebook container, however.)

```{r}
library(survey)
```

```{r}
anes_2016_vprevote_desgn <- svydesign(id = ~psu_f2f,
                                       strata = ~strat_f2f,
                                       weights = ~pre_w_f2f,
                                       data = anes_2016_vprevote,
                                       nest = TRUE)
save(anes_2016_vprevote_desgn,file="anes-2016-vprevote-design.RData")
```

We collect the electoral results of 2012 to prepare poststratification.

```{r}
result.2012 = c(Obama  = 65915795,
                Romney = 60933504,
                # Other candidates are combined
                Other = sum(c(
                    Johson = 1275971,
                    Stein  =  469627,
                    Others =  490510
                )))
```

The number of non-voters is computed from the sum of the results and census
data on the population in voting age.

```{r}
result.2012 <- c(result.2012,
                 "No vote" = 235248000 - sum(result.2012)) 
```

```{r}
# Here we collect the results for 2016
result.2016 <- c(Clinton = 65853514,
                 Trump   = 62984828,
                 Other   = sum(c(
                    Johnson  = 4489341, 
                    Stein    = 1457218,
                    McMullin =  731991,
                    Others   = 1154084 
                 )))
```

```{r}
result.2016 <- c(result.2016,
                 "No vote" = 250056000 - sum(result.2016))                 
```

The poststratification function expects population data to be in the form of
data frames:

```{r}
pop.vote16 <- data.frame(
    vote16=names(result.2016),
    Freq=result.2016)
```

```{r}
pop.recall12 <- data.frame(
    recall12=names(result.2012),
    Freq=result.2012/sum(result.2012)*sum(result.2016)
)
```

```{r}
save(pop.recall12,pop.vote16,file="popl-results.RData")
```

We poststratify the sample design object by recalled vote in 2012

```{r}
anes_2016_prevote_desgn_post <- postStratify(
    anes_2016_vprevote_desgn,~recall12,population=pop.recall12)
```

We compare the estimated percentages of 2012 votes:

```{r}
100*svymean(~recall12,design=anes_2016_vprevote_desgn)
```

```{r}
100*svymean(~recall12,design=anes_2016_prevote_desgn_post)
```

As should be expected, post-stratification eliminates the uncertainty about
2012 votes. It also corrects for turnout overreporting.


We now compare the estimated percentages of 2016 votes

```{r}
100*svymean(~vote16,design=anes_2016_vprevote_desgn)
```

```{r}
100*svymean(~vote16,design=anes_2016_prevote_desgn_post)
```

The percentages of Clinton voters and Trump voters are closer after
poststratification.


We save the poststratified data for later use.

```{r}
save(anes_2016_prevote_desgn_post,file="anes-2016-prevote-desgn-post.RData")
```
