# Constructing a survey design object from data of the 2016 American Election   Study.


The following makes use of the *memisc* package. You may need to install it from
[CRAN](https://cran.r-project.org/package=memisc) using the code
`install.packages("memisc")` if you want to run this on your computer. (The
package is already installed on the notebook container, however.)

```{r}
library(memisc)
```

The the code makes used of the data file "`anes_timeseries_2016.sav`", which is not included in the supporting material. In order to 
obtain this data file (and run this notebook successufully), you need to download them from 
the [ANES website for 2016](https://electionstudies.org/data-center/2016-time-series-stud/) and upload them to the virtual
machine that runs this notebook. To do this, 

1. open the file manager window of this site using [this link](/user-redirect/tree/05-social-science-surveys/)
2. use the button labelled "Upload" to upload the data set that you downloaded from the ANES website.
3. after uploading the file, it should appear in the list of files in the folder. Make sure that its name is`anes_timeseries_2016.sav`.

Note that the uploaded data will disappear, once you "Quit" the notebook (and the Jupyter instance).

```{r}
anes_2016_sav <- spss.file("anes_timeseries_2016.sav")
```

Loading a subset: Only pre-election waves and only
face-to-face interviews

```{r}
anes_2016_pre_work_ds <- subset(anes_2016_sav,
                                V160501 == 1,
                                select=c(
                                # According to docs, these are the
                                # sample weights for the
                                # face-to-face component
                                pre_w_f2f     = V160101f,
                                # Face-to-face strata    
                                strat_f2f     = V160201f,
                                psu_f2f       = V160202f,
                                pre_voted12   = V161005,
                                pre_recall12  = V161006,
                                pre_voted     = V161026,
                                pre_vote      = V161027,
                                pre_intov     = V161030,
                                pre_voteint   = V161031#,
                           ))
```

```{r}
library(magrittr) # For the '%<>%' operator
```

```{r}
anes_2016_pre_work_ds %<>% within({
    # Setting up recalled votes of 2012
    # Since a "default" value for the remaining conditions
    # is used, we use 'check.xor = FALSE' to avoid warnings.
    recall12 <- cases(
        'Did not vote' = 9 <- pre_voted12  == 2,
        'Obama'        = 1 <- pre_recall12 == 1,
        'Romney'       = 2 <- pre_recall12 == 2,
        'Other'        = 3 <- pre_recall12 == 5,
        'Inap'         = 99 <- TRUE, check.xor = FALSE
    )
    # Early voters 
    vote16_1 <- cases(
        'Clinton' = 1 <- pre_voted == 1 & pre_vote == 1,
        'Trump'   = 2 <- pre_voted == 1 & pre_vote == 2,
        'Other'   = 3 <- pre_voted == 1 & pre_vote %in% 3:5,
        'Inap'    = 99 <- TRUE, check.xor = FALSE)
    # Vote intentions
    vote16 <- cases(
        'Clinton' = 1 <- pre_intov == 1 & pre_voteint == 1,
        'Trump'   = 2 <- pre_intov == 1 & pre_voteint == 2,
        'Other'   = 3 <- pre_intov == 1 & pre_voteint %in% 3:6,
        'Will not vote/Not registered' = 8 <- pre_intov %in% c(-1,2),
        'Inap'    = 99 <- TRUE, check.xor = FALSE)
    vote16[] <- ifelse(vote16 == 99 & vote16_1 != 99,
                       vote16_1,
                       vote16)
    measurement(pre_w_f2f) <- "ratio"
})
```

```{r}
anes_2016_prevote <- as.data.frame(anes_2016_pre_work_ds)
save(anes_2016_prevote,file="anes-2016-prevote.RData")
```

```{r}
#Unweighted crosstable
xtabs(~ vote16 + recall12,
      data=anes_2016_prevote)
```

The following makes use of the *survey* package. You may need to install it from
[CRAN](https://cran.r-project.org/package=survey) using the code
`install.packages("survey")` if you want to run this on your computer. (The
package is already installed on the notebook container, however.)

```{r}
library(survey)
```

```{r}
anes_2016_prevote_desgn <- svydesign(id = ~psu_f2f,
                                     strata = ~strat_f2f,
                                     weights = ~pre_w_f2f,
                                     data = anes_2016_prevote,
                                     nest = TRUE)
anes_2016_prevote_desgn
```

In order to later make use of the survey design object, we save it into a file.

```{r}
save(anes_2016_prevote_desgn,file="anes-2016-prevote-desgn.RData")
```

We reduce the digits after dot ...

```{r}
ops <- options(digits=2)
(tab <- svytable(~ vote16 + recall12,
                 design = anes_2016_prevote_desgn))
```

and drop counts of non-valid responses before
we compute percentages.

```{r}
percentages(vote16 ~ recall12, data=tab[-6,-5])
```

```{r}
options(ops) # To undo the change in the options.
```

Here we compute a *F*-test of independence with the table, which uses the
Rao-Scott second-order correction with a Satterthwaite approximation of the
denominator degrees of freedom is used.

```{r}
summary(tab)
```

The more conventional Pearson-Chi-squared test adjusted with a design-effect
estimate is obtained by a slight modification.

```{r}
summary(tab, statistic="Chisq")
```
