# Constructing a survey design object from a data frame


First we activate the *survey* package. You may need to install it from [CRAN](https://cran.r-project.org/package=survey) using the code `install.packages("survey")` before this if you try running this on your computer. (Package is already installed on the notebook container, however.)

```{r}
library(survey)
```

Next we make the `NHANES` data set available (which comes with the *survey*
package)

```{r}
data(nhanes)
```

Now we can take a look at the data set, it has 7 variables and 8581 observations

```{r}
head(nhanes)
```

```{r}
nrow(nhanes)
```

According to the documentation, the primary sampling units are identified by
the variable `SDMVPSU`, the strata from which the PSUs are drawn are
identified by the variable `SDMVSTRA`, and the sample weights are `WTMEC2YR`.
The sum of the sample weights corresponds to the population size:

```{r}
with(nhanes,sum(WTMEC2YR))
```

Here were create "ordinary" sampling weights as they are common in social
science data sets:

```{r}
nhanes <- within(nhanes,{
    smplw <- WTMEC2YR/sum(WTMEC2YR)*nrow(nhanes)
})
```

We now create two survey design objects, one with the "population size"
weights and one with the "sample size" weights:

```{r}
design_pop <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA,
                            weights = ~WTMEC2YR, data = nhanes)
```

First attempt fails: the cluster numbers are not nested in the strata.
We try again with `nest = TRUE`

```{r}
design_pop <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA,
                        weights = ~WTMEC2YR, data = nhanes,
                        nest = TRUE)
design_smpl <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA,
                         weights = ~smplw, data = nhanes,
                         nest = TRUE)
```

We first estimate the population proportions with high cholesterol `(HI_CHOL==1)`

```{r}
svymean(~HI_CHOL, design=design_pop, na.rm=TRUE)
```

```{r}
svymean(~HI_CHOL, design=design_smpl, na.rm=TRUE)
```

We secondly estimate the number of those with high cholesterol `(HI_CHOL==1)` in
the population:

```{r}
svytotal(~HI_CHOL, design=design_pop, na.rm=TRUE)
```

```{r}
svytotal(~HI_CHOL, design=design_smpl, na.rm=TRUE)
```

Obviously, we need the "population size" weights for an unbiased estimate of
the population total, otherwise we just get a sample total.


Using the "population size" weights, we can reconstruct the sizes of the
population strata:

```{r}
nhanes <- within(nhanes,{
    strata_size <- ave(WTMEC2YR,SDMVSTRA,FUN=sum)
})
design_pop <- svydesign(id = ~SDMVPSU, strata = ~SDMVSTRA,
                        weights = ~WTMEC2YR, data = nhanes,
                        nest = TRUE, fpc = ~ strata_size)
design_pop
```

Of course, usually its the other way round: starting with the strata and the
cluster IDs, the sampling probabilities and sampling weights are computed.
