# Comparing poststratification, raking, and calibration with ANES data

```{r}
options(jupyter.rich_display=FALSE) # Create output as usual in R
```

The following makes use of the packages *survey* and *memisc*. You may need to
install them from [CRAN](https://cran.r-project.org) using the code
`install.packages(c("survey","memisc"))` if you want to run this on your computer. (The packages are already installed on the notebook container, however.)

```{r}
library(survey)
```

```{r}
library(memisc)
```

This loads data files created in earlier examples.

```{r}
load("anes-2016-vprevote-design.RData")
load("anes-2016-prevote-desgn-post.RData")
load("anes-2016-prevote-desgn-rake.RData")
load("anes-2016-prevote-desgn-calib.RData")
```

Let's compare the effect of poststratification and raking on the relation
between variables.

First, we create a table from the data with valid responses about voting
behaviour in 2012 and 2016.

```{r}
tab <- svytable(~ vote16 + recall12,
                 design = anes_2016_vprevote_desgn)
percentages(vote16 ~ recall12, data=tab)
```

Second, we create a table from the poststatified data.

```{r}
tab_post <- svytable(~ vote16 + recall12,
                 design = anes_2016_prevote_desgn_post)
percentages(vote16 ~ recall12, data=tab_post)
```

Third, we create a table from the raked data.

```{r}
tab_rak <- svytable(~ vote16 + recall12,
                    design = anes_2016_prevote_desgn_rake)
percentages(vote16 ~ recall12, data=tab_rak)
```

Fourth, we create a table from the calibrated data

```{r}
tab_calib <- svytable(~ vote16 + recall12,
                    design = anes_2016_prevote_desgn_calib)
percentages(vote16 ~ recall12, data=tab_calib)
```

Poststratification does not alter percentages that are conditional on the
variable used for poststratification. Yet raking does change the conditional percentages.


To examine whether raking affects relations between recalled vote in 2012 and
vote in 2016 we compute log-odds ratios:

```{r}
log.odds <- function(x) log((x[1,1]/x[1,2])/(x[2,1]/x[2,2]))
```

Log-odds ratios are a way to describe the relation between two dichotomous
variables. Like correlations between continuous variables they are not
affected by the marginal distribution.

```{r}
log.odds(tab)
```

```{r}
log.odds(tab_post)
```

```{r}
log.odds(tab_rak)
```

```{r}
log.odds(tab_calib)
```

Clearly, both poststratfication and raking leaves log-odds ratios
unaffected. Calibration has an effect, but this appears to be minor (at least
in the present case).
